% Latex-resume-code

\documentclass[a4paper]{MagicalCV}


% Removing page numbers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

% Change the geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Defining your colors
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-purple}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% start document
\begin{document}

% Last update time
\lastupdated

% Title name
\namesection{Rishabh }{Jain}{
\phone{+91-9557768322} \email{\href{mailto:jain.51@iitj.ac.in}{jain.51@iitj.ac.in}}}

% Column one
\begin{minipage}[t]{0.33\textwidth} 

% Education
\cvsection{Education} 
\newline
\subsection{IIT JODHPUR}
\newline
\descript{B.TECH IN Electrical Engg.  2020-2024*}
Cum. GPA :
\textbf{ 7.64}
(till 4th Sem)
\newline
\subsection{SENIOR SECONDARY}
%\descript{BTech in Computer Science}
%\cvevent{Sep 2020}{Gwalior, MP} 
New St. Stephen’s Public School, Agra |
2019 Percentage: {\bf 93.8}
\newline
\subsection{SECONDARY}
%\descript{BTech in Computer Science}
%\cvevent{Sep 2020}{Gwalior, MP} 
New St. Stephen’s Public School, Agra |
2017 CGPA: {\bf 9.2}


\sectionsep

% Links
\cvsection{Links}\\
\linkedin{Linkedin} \href{https://www.linkedin.com/in/rishabh-jain-653611237/}{\bf Rishabh Jain}
\github{GitHub} \href{https://github.com/struglingcoder/}{\bf struglingcoder}\\
\textbullet{} \codechef{Codechef} \href{https://www.codechef.com/users/struglingcoder/}{\bf struglingcoder}\\
\newline
\textbullet{}\codeforces{Codeforces}
\href{https://codeforces.com/profile/strugling_coder/}{\bf struglingcoder}

\sectionsep

% Coursework
\cvsection{Coursework}\\
\bigskip
\subsection{UnderGraduate}

 \textbullet{} Data Structure and Algorithms \\
 \textbullet{} Pattern Recognition and \\ \hspace{0.14cm} Machine Learning \\
 \textbullet{} Probability, Statistics and\\ \hspace{0.14cm} Stochastic process \\
 \textbullet{} Introduction to Computer\\ \hspace{0.14cm} Science \\
  \textbullet{} Foundations of Quantum\\ \hspace{0.14cm} Information \\ 
  \textbullet{} Digital Design \\
  \textbullet{} Circuit Theory \\
  \textbullet{} Engineering Design \\
  \textbullet{} Signal and Systems
%Artificial Intelligence \\
%Machine Learning \\
%Statistical Learning \\ 
%\textbf{Dissertation: }
%Machine learning methods for solubility prediction in chemical experiments
\sectionsep

% Skills
\cvsection{Skills}\\
\bigskip
\subsection{Programming}
\descript{Proficient}
 \textbullet{}   C++ \textbullet{} Python
 \newline
 \descript{Familiar}
 \textbullet{} Java \textbullet{} HTML \textbullet{}
CSS \newline \textbullet{} Javascript \textbullet{} Matlab \textbullet{} Latex
\sectionsep
\subsection{Miscellaneous}
 \textbullet{} Competitive Programming \newline \textbullet{} Machine Learning \newline \textbullet{} Sklearn \textbullet{} numpy \textbullet{} pandas\newline \textbullet{} Public Speaking
 \newline
 \textbullet{} Stock Market Investor
\sectionsep
% Honors
%\cvsection{Honors} 

%\subsection{Excellence Scholarship}
%\descript{University of leeds}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%
%\sectionsep

%\subsection{Industrial Visit}
%\descript{Infosys Pune}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%I was as one of the students for industrial training, where 28 students were chosen out of 2000.
%\sectionsep

% Column two
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

\cvsection{Experience}\\
\newline
\runsubsection{{\textbf{SDE INTERNSHIP | Getout Travel  }}}\\
\descript{| OpenCV, NodeJS, Python, ReactNative or Native |}
\cvevent{29 sep 2022 – present}{Remote}\\ 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\begin{small}
\item {\textbf{Getout Travel}} a digital travel eco system for all businesses, individuals, and service providers.
\item The \textbf{SDE-Intern} is responsible for developing \textbf{web applications} and
\textbf{software} from requirements and specifications.
\item Participates as \textbf{technical intern} to analyze
\textbf{technical} system problems, and \textbf{designs} and \textbf{implements} effective solutions.
\end{small}
\end{tightemize}
\sectionsep
% Experience
\cvsection{Projects}
\newline
\newline
%\runsubsection{Rerouting application development for EVs|} \\
\runsubsection{Rerouting application development for EVs| }\\
\descript{Design Credit Project Dr. Ravi Yadav , IITJ |

\href{https://ev-rerouting.herokuapp.com//}{ Website link  |}
\hspace{0.3cm}
\href{https://github.com/struglingcoder/Rerouting-application-development-for-EVs-/}{ Github Repository  |}}


\cvevent{Jan 2022 – April 2022}{Jodhpur, Raj.} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\begin{small}
\item Converted {\bf real world} data of latitude and longitude into
{\bf graph nodes}. 
\item Used {\bf Dijkstra’s algorithm} to find the {\bf shortest path} between Source location and final destination.
\item Considering the factors {\bf Current charging status} and
location of {\bf  Charging station}.
\item Displayed the optimal path in {\bf  google map }Highlighting
{\bf  the optimal route.}
\end{small}
\end{tightemize}
\sectionsep

\runsubsection{Heart Failure Detection |} \\
\descript{building a Heart
Failure Predictor | Machine Learning |Course Project
Dr. Richa Singh, IITJ |
\href{https://github.com/struglingcoder/prml-course-project/}{\hspace{0.3cm}| Github Repository  |}}
\cvevent{Jan 2022 – Apr 2022}{Jodhpur, Raj}\\ 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\begin{small}
\item Used {\bf SVM, XGBoost } and other various classification algorithms to predict heart failure.
\item Tune the {\bf Hyper parameters} of Models which have higher {\bf  accuracy score}.
\item Used {\bf pyplot} from {\bf matplotlib} library to visualize the accuracy score of the tuned parameters.
\end{small}
\end{tightemize}
\sectionsep

\runsubsection{Bitcoin Price Prediction| } \\
\descript{building a Bitcoin
Price Predictor Machine Learning Course Bonus
Project Dr. Richa Singh, IITJ | \href{https://github.com/struglingcoder/prml_bonus_project/}{\hspace{0.3cm}| Github Repository  |}}
\cvevent{Jan 2022 – Apr 2022}{Jodhpur, Raj} 
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\begin{small}
\item Used {\bf LinearRegressor , AdaBoostRegressor} and other various regression algorithms to predict {\bf  Bitcoin } price.
\item Tune the {\bf Hyper parameters} of various Regression Models by scratch.
\item  Used {\bf pyplot} from {\bf matplotlib} library to visualize the {\bf  MSE} of the tuned parameters.
\end{small}
\end{tightemize}
\sectionsep


% Competitions
\cvsection{ACHIEVEMENTS}
\bigskip
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\begin{small}
\item  {\bf 2019  \hspace{1cm} 1st Rank} \hspace{0.9cm} Secured 1st Rank in {\bf Class XII} ( School Topper )
\item  {\bf 2020  \hspace{1cm} Top 1 percent} \hspace{0.37cm} Among Top 1 percent in {\bf JEE Advanced}
\item  {\bf 2020  \hspace{1cm} 6th Rank} \hspace{1.17cm} Secured {\bf Department rank-6 } in first year

\item  {\bf 2021  \hspace{1cm} Branch Change} \hspace{0.27cm} Succeeded in {\bf  department
change } from  Chemical\\ \hspace{4.65cm}to Electrical
\end{small}
\end{tightemize}
\sectionsep


% Recent Projects
\cvsection{EXTRACURRICULARS} \\
\bigskip
\begin{small}
 \textbullet{} Registerd District {\bf Cricket} Player ( Agra, Uttar Pradesh)\\
 \textbullet{} Core Member of {\bf Drama Society} of IIT Jodhpur, {\bf Dramebaaz}\\
 \textbullet{} {\bf Co-ordinator} in the largest annual Inter College {\bf Sports Fest} of IIT Jodhpur, {\bf Varchas}\\
 \textbullet{} Secured {\bf 4th Rank} in inter-Hostel
poetry Competition , {\bf Spandan}
\end{small}
\sectionsep

%\runsubsection{Study of the behaviour of Serial Killers’} \\
%\descript{University of Leeds}
%\cvevent{Nov 2021 – Dec 2021}{Leeds, UK} 
%The study of the behaviour of serial killers with different motives such as %Convenience (did not want children/spouse), Enjoyment or Power and Escape or %avoiding arrest.
\end{minipage} 
\end{document}  
